---
title: "html report"
date: "`r Sys.Date()`"
bibliography: refer.bib
csl: nature-methods.csl
link-citations: true
nocite: "@*"
output: 
  bookdown::html_document2:
    toc: true
    fig_caption: true 
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  cache = TRUE
)

library(ggplot2, help, pos = 2, lib.loc = NULL)
```

# cite

cite ggplot2[@ggplot2]  
cite r-base[@r-base]

# cross-reference

You can use cross reference for table, figure and expression. \@ref(fig:plot-cor) show the cor plot of mtcars dataset.
If you want to cross-reference, those elements should have label, because reference dependend on these label envioment, and figure shoul have caption(`fig.cap`)

## correlation plot

```{r plot-cor, fig.show="hold", fig.cap = "(ref:mtcar-cor)"}
plot(mtcars)
```

(ref:mtcar-cor) this is figure caption


## mtcars table

table \@ref(tab:tab-mtcars) show the mtcars table.

```{r tab-mtcars}
head(mtcars) |>  kableExtra::kbl(caption = "this is table caption") |>
  kableExtra::kable_classic(full_width = FALSE, html_font = "Cambria")
```


# References

<div id="refs"></div>

# (APPENDIX) Appendix {-} 

[More on html table](https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html)  
[More on cite style language](https://www.zotero.org/styles)
[more on bib]

# More information

This will be Appendix A.

# One more thing

This will be Appendix B.

